### 2017-01-14 sec-results.tex
Switch to JEDM theme for a EDM 2017 Journal Track submission.
Update all figures for adjusted font size.

\newcommand{\textretrieval}{\preprintonly{textretrieval-001}%
    \finalonly{textretrieval-001}%
    \submissiononly{moocname1-00X}}

\newcommand{\sustain}{\preprintonly{sustain-001}%
    \finalonly{sustain-001}%
    \submissiononly{moocname2-00X}}

\newcommand{\UIUC}{\preprintonly{UIUC}%
    \finalonly{UIUC}%
    \submissiononly{(redacted University)}}

@@

\begin{figure*}
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \includegraphics[width=\textwidth]{figures/text-6state/state0.png}
    \caption{An example ``quiz taking'' state.}
    \label{fig:practice-quiz-state}
  \end{subfigure}%
  \begin{subfigure}[t]{0.5\textwidth}
    \includegraphics[width=\textwidth]{figures/text-6state/state1.png}
    \caption{An example ``lecture viewing'' state.}
    \label{fig:lecture-viewing-state}
  \end{subfigure}
  \caption{Two example states found by the 6-state TL-HMM.}
  \label{fig:states}
\end{figure*}

@@

\begin{figure*}
  \centering
  \begin{tabular}{cccc}
    \textbf{State 0 (Wiki)} & \textbf{State 1 (Lecture)}
    & \textbf{State 2 (Thread View)} & \textbf{State 3 (Lecture/Wiki)}\\\hline
    \includegraphics[width=0.22\textwidth]{figures/text-2state/state0.png}
    &
    \includegraphics[width=0.22\textwidth]{figures/text-2state/state1.png}\\
    \includegraphics[width=0.22\textwidth]{figures/text-3state/state0.png}
    &
    \includegraphics[width=0.22\textwidth]{figures/text-3state/state1.png}
    &
    \includegraphics[width=0.22\textwidth]{figures/text-3state/state2.png}\\
    \includegraphics[width=0.22\textwidth]{figures/text-4state/state0.png}
    &
    \includegraphics[width=0.22\textwidth]{figures/text-4state/state1.png}
    &
    \includegraphics[width=0.22\textwidth]{figures/text-4state/state2.png}
    &
    \includegraphics[width=0.22\textwidth]{figures/text-4state/state3.png}
  \end{tabular}
  \caption{The evolution of states for increasing $K$ for the
  \protect\textretrieval{} MOOC.\ State ``names'' indicate the highest
  probability action(s) within the state.} % I don't know why \protect is needed
  \label{fig:text-state-evolution}
\end{figure*}

In Figure~\ref{fig:text-state-evolution} we see the evolution of the latent
state representations found for the \textretrieval{} MOOC\footnote{Due to
space constraints, the graphs are quite small, but the states are in the
same positions as they were in previous figures to aid interpretation.}.
With $K=2$ we uncover a video watching pattern (state 1) and a course
material browsing pattern (state 0). However, we can see that when $K=3$ we
are able to uncover a new pattern involving forum behavior in state 3
(notice the node sizes on the bottom right). As we increase $K$ to four, we
can see that state 1 splits into state 1 and state 3. These states appear
quite similar at a glance, but there are still some key differences. First,
we can see that state 1 now has a non-negligible forum component, whereas
state 3 has hardly any weight on the forum.

\begin{figure*}
  \centering
  \begin{tabular}{cccc}
    \textbf{State 0 (Wiki)}
    & \textbf{State 1 (Lecture/Wiki)}
    & \textbf{State 2 (Thread List)}
    & \textbf{State 3 (Thread View)}\\\hline
    \includegraphics[width=0.22\textwidth]{figures/sustain-2state/state0.png}
    &
    \includegraphics[width=0.22\textwidth]{figures/sustain-2state/state1.png}\\
    \includegraphics[width=0.22\textwidth]{figures/sustain-3state/state0.png}
    &
    \includegraphics[width=0.22\textwidth]{figures/sustain-3state/state2.png}
    &
    \includegraphics[width=0.22\textwidth]{figures/sustain-3state/state1.png}\\
    \includegraphics[width=0.22\textwidth]{figures/sustain-4state/state0.png}
    &
    \includegraphics[width=0.22\textwidth]{figures/sustain-4state/state3.png}
    &
    \includegraphics[width=0.22\textwidth]{figures/sustain-4state/state1.png}
    &
    \includegraphics[width=0.22\textwidth]{figures/sustain-4state/state2.png}
  \end{tabular}
  \caption{The evolution of states for increasing $K$ for the
  \protect\sustain{} MOOC.\ State ``names'' indicate the highest
  probability action(s) within a state.} % I don't know why \protect is needed
  \label{fig:sustain-state-evolution}
\end{figure*}

>>>>

\newcommand{\textretrieval}{textretrieval-001}

\newcommand{\sustain}{sustain-001}

\newcommand{\UIUC}{UIUC}

@@

\begin{figure*}
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \includegraphics[width=\textwidth]{figures/text-6state/state0.png}
    \caption{An example ``quiz taking'' state.}
    \label{fig:practice-quiz-state}
  \end{subfigure}%
  \begin{subfigure}[t]{0.5\textwidth}
    \includegraphics[width=\textwidth]{figures/text-6state/state1.png}
    \caption{An example ``lecture viewing'' state.}
    \label{fig:lecture-viewing-state}
  \end{subfigure}
  \caption{Two example states found by the 6-state TL-HMM. (The naming of
  these states reflects our own interpretation.)}
  \label{fig:states}
\end{figure*}

@@

\afterpage{%
\begin{landscape}
\begin{figure*}
  \centering
  \begin{tabular}{cccc}
    \textbf{State 0 (Wiki)} & \textbf{State 1 (Lecture)}
    & \textbf{State 2 (Thread View)} & \textbf{State 3 (Lecture/Wiki)}\\\hline
    \includegraphics[width=0.30\textwidth]{figures/text-2state/state0.png}
    &
    \includegraphics[width=0.30\textwidth]{figures/text-2state/state1.png}\\
    \includegraphics[width=0.30\textwidth]{figures/text-3state/state0.png}
    &
    \includegraphics[width=0.30\textwidth]{figures/text-3state/state1.png}
    &
    \includegraphics[width=0.30\textwidth]{figures/text-3state/state2.png}\\
    \includegraphics[width=0.30\textwidth]{figures/text-4state/state0.png}
    &
    \includegraphics[width=0.30\textwidth]{figures/text-4state/state1.png}
    &
    \includegraphics[width=0.30\textwidth]{figures/text-4state/state2.png}
    &
    \includegraphics[width=0.30\textwidth]{figures/text-4state/state3.png}
  \end{tabular}
  \caption{The evolution of states for increasing $K$ for the
  \protect\textretrieval{} MOOC.\ State ``names'' indicate the highest
  probability action(s) within the state.} % I don't know why \protect is needed
  \label{fig:text-state-evolution}
\end{figure*}
\end{landscape}
}

\afterpage{%
\begin{landscape}
\begin{figure*}
  \centering
  \begin{tabular}{cccc}
    \textbf{State 0 (Wiki)}
    & \textbf{State 1 (Lecture/Wiki)}
    & \textbf{State 2 (Thread List)}
    & \textbf{State 3 (Thread View)}\\\hline
    \includegraphics[width=0.30\textwidth]{figures/sustain-2state/state0.png}
    &
    \includegraphics[width=0.30\textwidth]{figures/sustain-2state/state1.png}\\
    \includegraphics[width=0.30\textwidth]{figures/sustain-3state/state0.png}
    &
    \includegraphics[width=0.30\textwidth]{figures/sustain-3state/state2.png}
    &
    \includegraphics[width=0.30\textwidth]{figures/sustain-3state/state1.png}\\
    \includegraphics[width=0.30\textwidth]{figures/sustain-4state/state0.png}
    &
    \includegraphics[width=0.30\textwidth]{figures/sustain-4state/state3.png}
    &
    \includegraphics[width=0.30\textwidth]{figures/sustain-4state/state1.png}
    &
    \includegraphics[width=0.30\textwidth]{figures/sustain-4state/state2.png}
  \end{tabular}
  \caption{The evolution of states for increasing $K$ for the
  \protect\sustain{} MOOC.\ State ``names'' indicate the highest
  probability action(s) within a state.} % I don't know why \protect is needed
  \label{fig:sustain-state-evolution}
\end{figure*}
\end{landscape}
}

In Figure~\ref{fig:text-state-evolution} we see\footnote{Due to space
constraints, the graphs are quite small, but the states are in the same
positions as they were in previous figures to aid interpretation.} the
evolution of the latent state representations found for the
\textretrieval{} MOOC.  With $K=2$ we uncover a video watching pattern
(state 1) and a course material browsing pattern (state 0). However, we can
see that when $K=3$ we are able to uncover a new pattern involving forum
behavior in state 3 (notice the node sizes on the bottom right). As we
increase $K$ to four, we can see that state 1 splits into state 1 and state
3. These states appear quite similar at a glance, but there are still some
key differences. First, we can see that state 1 now has a non-negligible
forum component, whereas state 3 has hardly any weight on the forum.
